% !TeX spellcheck = pl_PL
% \appendixpage
% \addappheadtotoc

\appendix
\begin{appendices}
    \chapter{Lista pytań w ankiecie StackOverflow w roku 2017}\label{app:dod1}
    \begin{itemize}
        \item CareerSatisfaction,Career satisfaction rating
        \item JobSatisfaction,Job satisfaction rating
        \item JobSeekingStatus,Which of the following best describes your current job-seeking status?
        \item DeveloperType,Which of the following best describe you?
        \item YearsCodedJob,For how many years have you coded as part of your job?
        \item Country,In which country do you currently live?
        \item FormalEducation,Which of the following best describes the highest level of formal education that you've completed?
        \item EmploymentStatus,Which of the following best describes your current employment status?
        \item MajorUndergrad,Which of the following best describes your main field of study (aka 'major') in college or university/for your undergraduate studies?
        \item HaveWorkedLanguage,"Which of the following languages have you done extensive development work in over the past year, and which do you want to work in over the next year?"
        \item Gender,Which of the following do you currently identify as?
        \item CompanySize,"In terms of the number of employees, how large is the company or organization you work for?"
        \item HighestEducationParents,What is the highest level of education received by either of your parents?
        \item HaveWorkedFramework,"Which of the following libraries, frameworks, and tools have you done extensive development work in over the past year, and which do you want to work in over the next year?"
        \item HaveWorkedDatabase,"Which of the following database technologies have you done extensive development work in over the past year, and which do you want to work in over the next year?"
        \item HaveWorkedPlatform,"Which of the following platforms have you done extensive development work for over the past year, and which do you want to work on over the next year?"
        \item ProgramHobby,Do you program as a hobby or contribute to open source projects?
        \item University,"Are you currently enrolled in a formal, degree-granting college or university program?"
        \item YearsProgram,How long has it been since you first learned how to program?
        \item WebDeveloperType,Which of the following best describes you as a Web developer?
        \item MobileDeveloperType,For which of the following platforms do you develop mobile applications?
        \item NonDeveloperType,Which of the following describe you?
        \item ProblemSolving,I love solving problems
        \item BuildingThings,Building things is very rewarding
        \item LearningNewTech,Learning new technologies is fun
        \item BoringDetails,I tend to get bored by implementation details
        \item JobSecurity,Job security is important to me
        \item DiversityImportant,Diversity in the workplace is important
        \item AnnoyingUI,It annoys me when software has a poor UI
        \item FriendsDevelopers,"Most of my friends are developers, engineers, or scientists"
        \item RightWrongWay,There's a right and a wrong way to do everything
        \item UnderstandComputers,"Honestly, there's a lot about computers that I just don't understand"
        \item SeriousWork,I take my work very seriously
        \item InvestTimeTools,I invest a lot of time into the tools I use
        \item WorkPayCare,"I don't really care what I work on, so long as I'm paid well"
        \item KinshipDevelopers,I feel a sense of kinship to other developers
        \item ChallengeMyself,I like to challenge myself
        \item CompetePeers,I think of myself as competing with my peers
        \item ChangeWorld,I want to change the world
        \item LastNewJob,When was the last time that you took a job with a new employer?
        \item ImportantHiringAlgorithms,"Congratulations! You've just been put in charge of technical recruiting at Globex, a multinational high- tech firm. This job comes with a corner office, and you have an experienced staff of recruiters at your disposal. They want to know what they should prioritize when recruiting software developers. How important should each of the following be in Globex's hiring process? Knowledge of algorithms and data structures"
        \item ImportantHiringTechExp,"Congratulations! You've just been put in charge of technical recruiting at Globex, a multinational high- tech firm. This job comes with a corner office, and you have an experienced staff of recruiters at your disposal. They want to know what they should prioritize when recruiting software developers. How important should each of the following be in Globex's hiring process? Experience with specific tools (libraries, frameworks, etc.) used by the employer"
        \item ImportantHiringCommunication,"Congratulations! You've just been put in charge of technical recruiting at Globex, a multinational high- tech firm. This job comes with a corner office, and you have an experienced staff of recruiters at your disposal. They want to know what they should prioritize when recruiting software developers. How important should each of the following be in Globex's hiring process? Communication skills"
        \item ImportantHiringOpenSource,"Congratulations! You've just been put in charge of technical recruiting at Globex, a multinational high- tech firm. This job comes with a corner office, and you have an experienced staff of recruiters at your disposal. They want to know what they should prioritize when recruiting software developers. How important should each of the following be in Globex's hiring process? Contributions to open source projects"
        \item ImportantHiringPMExp,"Congratulations! You've just been put in charge of technical recruiting at Globex, a multinational high- tech firm. This job comes with a corner office, and you have an experienced staff of recruiters at your disposal. They want to know what they should prioritize when recruiting software developers. How important should each of the following be in Globex's hiring process? Experience with specific project management tools & techniques"
        \item ImportantHiringCompanies,"Congratulations! You've just been put in charge of technical recruiting at Globex, a multinational high- tech firm. This job comes with a corner office, and you have an experienced staff of recruiters at your disposal. They want to know what they should prioritize when recruiting software developers. How important should each of the following be in Globex's hiring process? Previous companies worked at"
        \item ImportantHiringTitles,"Congratulations! You've just been put in charge of technical recruiting at Globex, a multinational high- tech firm. This job comes with a corner office, and you have an experienced staff of recruiters at your disposal. They want to know what they should prioritize when recruiting software developers. How important should each of the following be in Globex's hiring process? Previous job titles held"
        \item ImportantHiringEducation,"Congratulations! You've just been put in charge of technical recruiting at Globex, a multinational high- tech firm. This job comes with a corner office, and you have an experienced staff of recruiters at your disposal. They want to know what they should prioritize when recruiting software developers. How important should each of the following be in Globex's hiring process? Educational credentials (e.g. schools attended, specific field of study, grades earned)"
        \item ImportantHiringRep,"Congratulations! You've just been put in charge of technical recruiting at Globex, a multinational high- tech firm. This job comes with a corner office, and you have an experienced staff of recruiters at your disposal. They want to know what they should prioritize when recruiting software developers. How important should each of the following be in Globex's hiring process? Stack Overflow reputation"
        \item ImportantHiringGettingThingsDone,"Congratulations! You've just been put in charge of technical recruiting at Globex, a multinational high- tech firm. This job comes with a corner office, and you have an experienced staff of recruiters at your disposal. They want to know what they should prioritize when recruiting software developers. How important should each of the following be in Globex's hiring process? Track record of getting things done"
        \item Overpaid,"Compared to your estimate of your own market value, do you think you are…?"
        \item EducationImportant,"Overall, how important has your formal schooling and education been to your career success?"
        \item EducationTypes,"Outside of your formal schooling and education, which of the following have you done?"
        \item SelfTaughtTypes,"You indicated that you had taught yourself a programming technology without taking a course. What resources did you use to do that? If you've done it more than once, please think about the most recent time you've done so."
        \item CousinEducation,"Let's pretend you have a distant cousin. They are 24 years old, have a college degree in a field not related to computer programming, and have been working a non-coding job for the last two years. They want your advice on how to switch to a career as a software developer. Which of the following options would you most strongly recommend to your cousin?"
        \item Methodology,Which of the following methodologies do you have experience working in?
        \item VersionControl,"What version control system do you use? If you use several, please choose the one you use most often."
        \item CheckInCode,"Over the last year, how often have you checked-in or committed code?"
        \item ShipIt,It's better to ship now and optimize later
        \item OtherPeoplesCode,Maintaining other people's code is a form of torture
        \item ProjectManagement,Most project management techniques are useless
        \item EnjoyDebugging,I enjoy debugging code
        \item InTheZone,I often get “into the zone” when I'm coding
        \item DifficultCommunication,I have difficulty communicating my ideas to my peers
        \item CollaborateRemote,It's harder to collaborate with remote peers than those on site
        \item AuditoryEnvironment,"Suppose you're about to start a few hours of coding and have complete control over your auditory environment (music, background noise, etc.). What would you do?"
        \item MetricAssess,"Congratulations! The bosses at your new employer, E Corp, are allowing you to choose which metrics will be used to assess your individual performance in your role as a senior developer. Which metrics do you suggest to the E bosses?"
        \item StackOverflowFoundAnswer,"Over the last three months, approximately how often have you done each of the following on Stack Overflow? Found an answer that solved my coding problem"
        \item StackOverflowCopiedCode,"Over the last three months, approximately how often have you done each of the following on Stack Overflow? Copied a code example and pasted it into my codebase"
        \item StackOverflowAnswer,"Over the last three months, approximately how often have you done each of the following on Stack Overflow? Written a new answer to someone else's question"
        \item StackOverflowMetaChat,"Over the last three months, approximately how often have you done each of the following on Stack Overflow? Participated in community discussions on meta or in chat"
        \item StackOverflowCommunity,I feel like a member of the Stack Overflow community
        \item StackOverflowHelpful,The answers and code examples I get on Stack Overflow are helpful
        \item StackOverflowBetter,Stack Overflow makes the Internet a better place
        \item StackOverflowWhatDo,I don't know what I'd do without Stack Overflow
        \item HomeRemote,How often do you work from home or remotely?
        \item CompanyType,Which of the following best describes the type of company or organization you work for?
        \item AssessJobIndustry,"When you're assessing potential jobs to apply to, how important are each of the following to you? The industry that I'd be working in"
        \item AssessJobRole,"When you're assessing potential jobs to apply to, how important are each of the following to you? The specific role or job title I'd be applying for"
        \item AssessJobExp,"When you're assessing potential jobs to apply to, how important are each of the following to you? The experience level called for in the job description"
        \item AssessJobDept,"When you're assessing potential jobs to apply to, how important are each of the following to you? The specific department or team I'd be working on"
        \item AssessJobTech,"When you're assessing potential jobs to apply to, how important are each of the following to you? The languages, frameworks, and other technologies I'd be working with"
        \item AssessJobProjects,"When you're assessing potential jobs to apply to, how important are each of the following to you? How projects are managed at the company or organization"
        \item AssessJobCompensation,"When you're assessing potential jobs to apply to, how important are each of the following to you? The compensation and benefits offered"
        \item AssessJobOffice,"When you're assessing potential jobs to apply to, how important are each of the following to you? The office environment I'd be working in"
        \item AssessJobCommute,"When you're assessing potential jobs to apply to, how important are each of the following to you? The amount of time I'd have to spend commuting"
        \item AssessJobRemote,"When you're assessing potential jobs to apply to, how important are each of the following to you? The opportunity to work from home/remotely"
        \item AssessJobLeaders,"When you're assessing potential jobs to apply to, how important are each of the following to you? The reputations of the company's senior leaders"
        \item AssessJobProfDevel,"When you're assessing potential jobs to apply to, how important are each of the following to you? Opportunities for professional development"
        \item AssessJobDiversity,"When you're assessing potential jobs to apply to, how important are each of the following to you? The diversity of the company or organization"
        \item AssessJobProduct,"When you're assessing potential jobs to apply to, how important are each of the following to you? How widely used or impactful the product or service I'd be working on is"
        \item AssessJobFinances,"When you're assessing potential jobs to apply to, how important are each of the following to you? The financial performance or funding status of the company or organization"
        \item ImportantBenefits,"When it comes to compensation and benefits, other than base salary, which of the following are most important to you?"
        \item WorkStart,Suppose you could choose your own working hours for an 8-hour day. What time would you start work for the day? Please adjust the slider to the hour nearest your ideal start time. The box next to the slider will display your selection using a 24-hour clock
        \item WantWorkLanguage,"Which of the following languages have you done extensive development work in over the past year, and which do you want to work in over the next year?"
        \item WantWorkFramework,"Which of the following libraries, frameworks, and tools have you done extensive development work in over the past year, and which do you want to work in over the next year?"
        \item WantWorkDatabase,"Which of the following database technologies have you done extensive development work in over the past year, and which do you want to work in over the next year?"
        \item WantWorkPlatform,"Which of the following platforms have you done extensive development work for over the past year, and which do you want to work on over the next year?"
        \item EquipmentSatisfiedMonitors,"Thinking about your main coding workstation, how satisfied are you with each of the following? Monitors/screens (number of, size, resolution)"
        \item EquipmentSatisfiedCPU,"Thinking about your main coding workstation, how satisfied are you with each of the following? Processing power (CPU and/or GPU)"
        \item EquipmentSatisfiedRAM,"Thinking about your main coding workstation, how satisfied are you with each of the following? Amount of RAM"
        \item EquipmentSatisfiedStorage,"Thinking about your main coding workstation, how satisfied are you with each of the following? Storage capacity"
        \item EquipmentSatisfiedRW,"Thinking about your main coding workstation, how satisfied are you with each of the following? Storage read/write speed"
        \item InfluenceInternet,How much influence do you have on purchasing decisions within your organization for each of the following? Internet bandwidth
        \item InfluenceWorkstation,How much influence do you have on purchasing decisions within your organization for each of the following? Your personal workstation hardware
        \item InfluenceHardware,How much influence do you have on purchasing decisions within your organization for each of the following? Personal workstation hardware for others in the company
        \item InfluenceServers,How much influence do you have on purchasing decisions within your organization for each of the following? Servers
        \item InfluenceTechStack,How much influence do you have on purchasing decisions within your organization for each of the following? Main technical stack of the company
        \item InfluenceDeptTech,How much influence do you have on purchasing decisions within your organization for each of the following? Technical stack used in your department
        \item InfluenceVizTools,"How much influence do you have on purchasing decisions within your organization for each of the following? Data analysis and visualization tools (e.g. Tableau, Looker)"
        \item InfluenceDatabase,How much influence do you have on purchasing decisions within your organization for each of the following? Database systems or solutions
        \item InfluenceCloud,How much influence do you have on purchasing decisions within your organization for each of the following? Cloud or serverless back-end solutions
        \item InfluenceConsultants,How much influence do you have on purchasing decisions within your organization for each of the following? Consultants
        \item InfluenceRecruitment,How much influence do you have on purchasing decisions within your organization for each of the following? Recruitment tools & platforms
        \item InfluenceCommunication,How much influence do you have on purchasing decisions within your organization for each of the following? Communication & collaboration tools
        \item Respondent,Respondent ID number
        \item ExCoderReturn,"You said before that you used to code as part of your job, but no longer do. To what extent do you agree or disagree with the following statements? If money weren't an issue, I would take a coding job again"
        \item ExCoderNotForMe,"You said before that you used to code as part of your job, but no longer do. To what extent do you agree or disagree with the following statements? Working as a developer just wasn't for me"
        \item ExCoderBalance,"You said before that you used to code as part of your job, but no longer do. To what extent do you agree or disagree with the following statements? I have better work-life balance now than I did as a developer"
        \item ExCoder10Years,"You said before that you used to code as part of your job, but no longer do. To what extent do you agree or disagree with the following statements? My career is going the way I thought it would 10 years ago"
        \item ExCoderBelonged,"You said before that you used to code as part of your job, but no longer do. To what extent do you agree or disagree with the following statements? When I was a developer, I didn't feel like I belonged with my colleagues"
        \item ExCoderSkills,"You said before that you used to code as part of your job, but no longer do. To what extent do you agree or disagree with the following statements? I don't think my coding skills are up to date"
        \item ExCoderWillNotCode,"You said before that you used to code as part of your job, but no longer do. To what extent do you agree or disagree with the following statements? I probably won't code for a living ever again"
        \item ExCoderActive,"You said before that you used to code as part of your job, but no longer do. To what extent do you agree or disagree with the following statements? I'm still active in the developer community"
        \item PronounceGIF,"How do you pronounce ""GIF""?"
        \item HoursPerWeek,"During a typical week, approximately how many hours do you spend on activities related to finding new job opportunities?Please adjust the slider to the appropriate number of hours. The box to the right will indicate the number of hours you have chosen."
        \item ClickyKeys,"If two developers are sharing an office, is it OK for one of them to get a mechanical keyboard with loud ""clicky"" keys?"
        \item JobProfile,"On which of the following sites do you maintain a profile, CV, or resumé?"
        \item ResumePrompted,"Think back to the last time you updated your resumé, CV, or an online profile on a job site. What prompted you to do so?"
        \item LearnedHiring,Think back to when you first applied to work for your current employer. Which of the following best describes how you learned that they were hiring for that particular job?
        \item Currency,"Which currency do you use day-to-day? If you're a globe-trotting digital nomad and the answer is “it's complicated,” please pick the one you're most comfortable estimating in."
        \item TabsSpaces,Tabs or spaces?
        \item TimeAfterBootcamp,You indicated previously that you went through a developer “bootcamp.” How long did it take you to get a full-time job as a developer after graduating?
        \item IDE,Which development environment(s) do you use regularly?
        \item StackOverflowDescribes,Which of the following best describes you?
        \item StackOverflowSatisfaction,Stack Overflow satisfaction
        \item StackOverflowDevices,Which of the following devices have you used to connect to Stack Overflow over the last three months?
        \item StackOverflowJobListing,"Over the last three months, approximately how often have you done each of the following on Stack Overflow? Seen a job listing I was interested in"
        \item StackOverflowCompanyPage,"Over the last three months, approximately how often have you done each of the following on Stack Overflow? Researched a potential employer by visiting its company page"
        \item StackOverflowJobSearch,"Over the last three months, approximately how often have you done each of the following on Stack Overflow? Searched for jobs"
        \item StackOverflowNewQuestion,"Over the last three months, approximately how often have you done each of the following on Stack Overflow? Asked a new question"
        \item StackOverflowAdsRelevant,The ads on Stack Overflow are relevant to me
        \item StackOverflowAdsDistracting,The ads on Stack Overflow are distracting
        \item StackOverflowModeration,The moderation on Stack Overflow is unfair
        \item StackOverflowMakeMoney,The people who run Stack Overflow are just in it for the money
        \item Race,Which of the following do you identify as?
        \item SurveyLong,This survey was too long
        \item QuestionsInteresting,The questions were interesting
        \item QuestionsConfusing,The questions were confusing
        \item InterestedAnswers,I'm interested in learning how other developers answered
        \item Salary,"What is your current annual base salary, before taxes, and excluding bonuses, grants, or other compensation?"
        \item ExpectedSalary,"You said before that you are currently learning how to program. When you have completed your studies, what annual salary do you expect to earn in your first job after graduation?"
        \item YearsCodedJobPast,For how many years did you code as part of your job?
        \item Professional,Which of the following best describes you?
    \end{itemize}


    \chapter{Lista pytań w ankiecie StackOverflow w roku 2018}\label{app:dod2}

    \begin{itemize}
        \item JobSatisfaction,"How satisfied are you with your current job? If you work more than one job, please answer regarding the one you spend the most hours on."
        \item CareerSatisfaction,"Overall, how satisfied are you with your career thus far?"
        \item JobSearchStatus,Which of the following best describes your current job-seeking status?
        \item ConvertedSalary,"Salary converted to annual USD salaries using the exchange rate on 2018-01-18, assuming 12 working months and 50 working weeks."
        \item DevType,Which of the following describe you? Please select all that apply.
        \item YearsCodingProf,For how many years have you coded professionally (as a part of your work)?
        \item Country,In which country do you currently reside?
        \item FormalEducation,Which of the following best describes the highest level of formal education that you’ve completed?
        \item Employment,Which of the following best describes your current employment status?
        \item UndergradMajor,You previously indicated that you went to a college or university. Which of the following best describes your main field of study (aka 'major')
        \item LanguageWorkedWith,"Which of the following programming, scripting, and markup languages have you done extensive development work in over the past year, and which do you want to work in over the next year?  (If you both worked with the language and want to continue to do so, please check both boxes in that row.)"
        \item Gender,"Which of the following do you currently identify as? Please select all that apply. If you prefer not to answer, you may leave this question blank."
        \item CompanySize,Approximately how many people are employed by the company or organization you work for?
        \item EducationParents,"What is the highest level of education received by either of your parents? If you prefer not to answer, you may leave this question blank."
        \item Age,"What is your age? If you prefer not to answer, you may leave this question blank."
        \item DatabaseWorkedWith,"Which of the following database environments have you done extensive development work in over the past year, and which do you want to work in over the next year?   (If you both worked with the database and want to continue to do so, please check both boxes in that row.)"
        \item PlatformWorkedWith,"Which of the following platforms have you done extensive development work for over the past year?   (If you both developed for the platform and want to continue to do so, please check both boxes in that row.)"
        \item FrameworkWorkedWith,"Which of the following libraries, frameworks, and tools have you done extensive development work in over the past year, and which do you want to work in over the next year?"
        \item Hobby,Do you code as a hobby?
        \item OpenSource,Do you contribute to open source projects?
        \item Student,"Are you currently enrolled in a formal, degree-granting college or university program?"
        \item YearsCoding,"Including any education, for how many years have you been coding?"
        \item HopeFiveYears,Which of the following best describes what you hope to be doing in five years?
        \item LastNewJob,When was the last time that you took a job with a new employer?
        \item EducationTypes,Which of the following types of non-degree education have you used or participated in? Please select all that apply.
        \item SelfTaughtTypes,"You indicated that you had taught yourself a programming technology without taking a course. What resources did you use to do that? If you’ve done it more than once, please think about the most recent time you’ve done so. Please select all that apply."
        \item HackathonReasons,You indicated previously that you had participated in an online coding competition or hackathon. Which of the following best describe your reasons for doing so?
        \item AgreeDisagree1,To what extent do you agree or disagree with each of the following statements? I feel a sense of kinship or connection to other developers
        \item AgreeDisagree2,To what extent do you agree or disagree with each of the following statements? I think of myself as competing with my peers
        \item AgreeDisagree3,To what extent do you agree or disagree with each of the following statements? I'm not as good at programming as most of my peers
        \item OperatingSystem,What is the primary operating system in which you work?
        \item NumberMonitors,How many monitors are set up at your workstation?
        \item Methodology,Which of the following methodologies do you have experience working in?
        \item VersionControl,What version control systems do you use regularly? Please select all that apply.
        \item CheckInCode,"Over the last year, how often have you checked-in or committed code?"
        \item EthicsChoice,Imagine that you were asked to write code for a purpose or product that you consider extremely unethical. Do you write the code anyway?
        \item EthicsReport,Do you report or otherwise call out the unethical code in question?
        \item EthicsResponsible,Who do you believe is ultimately most responsible for code that accomplishes something unethical?
        \item EthicalImplications,Do you believe that you have an obligation to consider the ethical implications of the code that you write?
        \item StackOverflowRecommend,How likely is it that you would recommend Stack Overflow overall to a friend or colleague? Where 0 is not likely at all and 10 is very likely.
        \item StackOverflowVisit,How frequently would you say you visit Stack Overflow?
        \item StackOverflowConsiderMember,Do you consider yourself a member of the Stack Overflow community?
        \item WakeTime,"On days when you work, what time do you typically wake up?"
        \item HoursComputer,"On a typical day, how much time do you spend on a desktop or laptop computer?"
        \item HoursOutside,"On a typical day, how much time do you spend outside?"
        \item SkipMeals,"In a typical week, how many times do you skip a meal in order to be more productive?"
        \item ErgonomicDevices,What ergonomic furniture or devices do you use on a regular basis? Please select all that apply.
        \item Exercise,"In a typical week, how many times do you exercise?"
        \item Dependents,"Do you have any children or other dependents that you care for? If you prefer not to answer, you may leave this question blank."
        \item LanguageDesireNextYear,"Which of the following programming, scripting, and markup languages have you done extensive development work in over the past year, and which do you want to work in over the next year?  (If you both worked with the language and want to continue to do so, please check both boxes in that row.)"
        \item DatabaseDesireNextYear,"Which of the following database environments have you done extensive development work in over the past year, and which do you want to work in over the next year?   (If you both worked with the database and want to continue to do so, please check both boxes in that row.)"
        \item PlatformDesireNextYear,"Which of the following platforms have you done extensive development work for over the past year?   (If you both developed for the platform and want to continue to do so, please check both boxes in that row.)"
        \item FrameworkDesireNextYear,"Which of the following libraries, frameworks, and tools have you done extensive development work in over the past year, and which do you want to work in over the next year?"
        \item AssessJob1,"Imagine that you are assessing a potential job opportunity. Please rank the following aspects of the job opportunity in order of importance (by dragging the choices up and down), where 1 is the most important and 10 is the least important. The industry that I'd be working in"
        \item AssessJob2,"Imagine that you are assessing a potential job opportunity. Please rank the following aspects of the job opportunity in order of importance (by dragging the choices up and down), where 1 is the most important and 10 is the least important. The financial performance or funding status of the company or organization"
        \item AssessJob3,"Imagine that you are assessing a potential job opportunity. Please rank the following aspects of the job opportunity in order of importance (by dragging the choices up and down), where 1 is the most important and 10 is the least important. The specific department or team I'd be working on"
        \item AssessJob4,"Imagine that you are assessing a potential job opportunity. Please rank the following aspects of the job opportunity in order of importance (by dragging the choices up and down), where 1 is the most important and 10 is the least important. The languages, frameworks, and other technologies I'd be working with"
        \item AssessJob5,"Imagine that you are assessing a potential job opportunity. Please rank the following aspects of the job opportunity in order of importance (by dragging the choices up and down), where 1 is the most important and 10 is the least important. The compensation and benefits offered"
        \item AssessJob6,"Imagine that you are assessing a potential job opportunity. Please rank the following aspects of the job opportunity in order of importance (by dragging the choices up and down), where 1 is the most important and 10 is the least important. The office environment or company culture"
        \item AssessJob7,"Imagine that you are assessing a potential job opportunity. Please rank the following aspects of the job opportunity in order of importance (by dragging the choices up and down), where 1 is the most important and 10 is the least important. The opportunity to work from home/remotely"
        \item AssessJob8,"Imagine that you are assessing a potential job opportunity. Please rank the following aspects of the job opportunity in order of importance (by dragging the choices up and down), where 1 is the most important and 10 is the least important. Opportunities for professional development"
        \item AssessJob9,"Imagine that you are assessing a potential job opportunity. Please rank the following aspects of the job opportunity in order of importance (by dragging the choices up and down), where 1 is the most important and 10 is the least important. The diversity of the company or organization"
        \item AssessJob10,"Imagine that you are assessing a potential job opportunity. Please rank the following aspects of the job opportunity in order of importance (by dragging the choices up and down), where 1 is the most important and 10 is the least important. How widely used or impactful the product or service I'd be working on is"
        \item AssessBenefits1,"Now, imagine you are assessing a job's benefits package. Please rank the following aspects of a job's benefits package from most to least important to you (by dragging the choices up and down), where 1 is most important and 11 is least important. Salary and/or bonuses"
        \item AssessBenefits2,"Now, imagine you are assessing a job's benefits package. Please rank the following aspects of a job's benefits package from most to least important to you (by dragging the choices up and down), where 1 is most important and 11 is least important. Stock options or shares"
        \item AssessBenefits3,"Now, imagine you are assessing a job's benefits package. Please rank the following aspects of a job's benefits package from most to least important to you (by dragging the choices up and down), where 1 is most important and 11 is least important. Health insurance"
        \item AssessBenefits4,"Now, imagine you are assessing a job's benefits package. Please rank the following aspects of a job's benefits package from most to least important to you (by dragging the choices up and down), where 1 is most important and 11 is least important. Parental leave"
        \item AssessBenefits5,"Now, imagine you are assessing a job's benefits package. Please rank the following aspects of a job's benefits package from most to least important to you (by dragging the choices up and down), where 1 is most important and 11 is least important. Fitness or wellness benefit (ex. gym membership, nutritionist)"
        \item AssessBenefits6,"Now, imagine you are assessing a job's benefits package. Please rank the following aspects of a job's benefits package from most to least important to you (by dragging the choices up and down), where 1 is most important and 11 is least important. Retirement or pension savings matching"
        \item AssessBenefits7,"Now, imagine you are assessing a job's benefits package. Please rank the following aspects of a job's benefits package from most to least important to you (by dragging the choices up and down), where 1 is most important and 11 is least important. Company-provided meals or snacks"
        \item AssessBenefits8,"Now, imagine you are assessing a job's benefits package. Please rank the following aspects of a job's benefits package from most to least important to you (by dragging the choices up and down), where 1 is most important and 11 is least important. Computer/office equipment allowance"
        \item AssessBenefits9,"Now, imagine you are assessing a job's benefits package. Please rank the following aspects of a job's benefits package from most to least important to you (by dragging the choices up and down), where 1 is most important and 11 is least important. Childcare benefit"
        \item AssessBenefits10,"Now, imagine you are assessing a job's benefits package. Please rank the following aspects of a job's benefits package from most to least important to you (by dragging the choices up and down), where 1 is most important and 11 is least important. Transportation benefit (ex. company-provided transportation, public transit allowance)"
        \item AssessBenefits11,"Now, imagine you are assessing a job's benefits package. Please rank the following aspects of a job's benefits package from most to least important to you (by dragging the choices up and down), where 1 is most important and 11 is least important. Conference or education budget"
        \item CommunicationTools,"Which of the following tools do you use to communicate, coordinate, or share knowledge with your coworkers? Please select all that apply."
        \item TimeFullyProductive,"Suppose a new developer with four years of experience, including direct experience working with your company's main technical stack, joined your team tomorrow. All other things being equal, how long would you expect it to take before they were fully productive and contributing at a typical level to your main code base?"
        \item Respondent,Randomized respondent ID number (not in order of survey response time)
        \item JobContactPriorities1,"Imagine that a company wanted to contact you about a job that is a good fit for you. Please rank your preference in how you are contacted (by dragging the choices up and down), where 1 is the most preferred and 5 is the least preferred. Telephone call"
        \item JobContactPriorities2,"Imagine that a company wanted to contact you about a job that is a good fit for you. Please rank your preference in how you are contacted (by dragging the choices up and down), where 1 is the most preferred and 5 is the least preferred. Email to my private address"
        \item JobContactPriorities3,"Imagine that a company wanted to contact you about a job that is a good fit for you. Please rank your preference in how you are contacted (by dragging the choices up and down), where 1 is the most preferred and 5 is the least preferred. Email to my work address"
        \item JobContactPriorities4,"Imagine that a company wanted to contact you about a job that is a good fit for you. Please rank your preference in how you are contacted (by dragging the choices up and down), where 1 is the most preferred and 5 is the least preferred. Message on a job site"
        \item JobContactPriorities5,"Imagine that a company wanted to contact you about a job that is a good fit for you. Please rank your preference in how you are contacted (by dragging the choices up and down), where 1 is the most preferred and 5 is the least preferred. Message on a social media site"
        \item JobEmailPriorities1,"Imagine that same company decided to contact you through email. Please rank the following items by how important it is to include them in the message (by dragging the choices up and down), where 1 is the most important and 7 is the least important. Details on the company I'd be working for"
        \item JobEmailPriorities2,"Imagine that same company decided to contact you through email. Please rank the following items by how important it is to include them in the message (by dragging the choices up and down), where 1 is the most important and 7 is the least important. Details on the specific department I'd be working for or product I'd be working on"
        \item JobEmailPriorities3,"Imagine that same company decided to contact you through email. Please rank the following items by how important it is to include them in the message (by dragging the choices up and down), where 1 is the most important and 7 is the least important. Specifics of why they think I'd be a good fit for the role (ex. my prior work history, projects on GitHub)"
        \item JobEmailPriorities4,"Imagine that same company decided to contact you through email. Please rank the following items by how important it is to include them in the message (by dragging the choices up and down), where 1 is the most important and 7 is the least important. Details of which technologies I'd be working with"
        \item JobEmailPriorities5,"Imagine that same company decided to contact you through email. Please rank the following items by how important it is to include them in the message (by dragging the choices up and down), where 1 is the most important and 7 is the least important. An estimate of the compensation range"
        \item JobEmailPriorities6,"Imagine that same company decided to contact you through email. Please rank the following items by how important it is to include them in the message (by dragging the choices up and down), where 1 is the most important and 7 is the least important. Information on the company's hiring process"
        \item JobEmailPriorities7,"Imagine that same company decided to contact you through email. Please rank the following items by how important it is to include them in the message (by dragging the choices up and down), where 1 is the most important and 7 is the least important. Details on the company's product development process"
        \item UpdateCV,"Think back to the last time you updated your resumé, CV, or an online profile on a job site. What is the main reason that you did so?"
        \item Currency,"Which currency do you use day-to-day? If your answer is complicated, please pick the one you're most comfortable estimating in."
        \item Salary,"What is your current gross salary (before taxes and deductions), in ${q://QID50/ChoiceGroup/SelectedChoicesTextEntry}? Please enter a whole number in the box below, without any punctuation. If you are paid hourly, please estimate an equivalent weekly, monthly, or yearly salary. If you prefer not to answer, please leave the box empty."
        \item SalaryType,"Is that salary weekly, monthly, or yearly?"
        \item CurrencySymbol,Three digit currency abbreviation.
        \item TimeAfterBootcamp,You indicated previously that you went through a developer training program or bootcamp. How long did it take you to get a full-time job as a developer after graduating?
        \item IDE,Which development environment(s) do you use regularly? Please check all that apply.
        \item AdBlocker,Do you have ad-blocking software installed on any computers you use regularly?
        \item AdBlockerDisable,"In the past month, have you disabled your ad blocker for any reason, even temporarily or for a specific website?"
        \item AdBlockerReasons,What are the reasons that you have disabled your ad blocker in the past month? Please select all that apply.
        \item AdsAgreeDisagree1,To what extent do you agree or disagree with the following statements: Online advertising can be valuable when it is relevant to me
        \item AdsAgreeDisagree2,To what extent do you agree or disagree with the following statements: I enjoy seeing online updates from companies that I like
        \item AdsAgreeDisagree3,To what extent do you agree or disagree with the following statements: I fundamentally dislike the concept of advertising
        \item AdsActions,Which of the following actions have you taken in the past month? Please select all that apply.
        \item AdsPriorities1,"Please rank the following advertising qualities in order of their importance to you (by dragging the choices up and down), where 1 is the most important, and 7 is the least important. The advertisement is relevant to me"
        \item AdsPriorities2,"Please rank the following advertising qualities in order of their importance to you (by dragging the choices up and down), where 1 is the most important, and 7 is the least important. The advertisement is honest about its goals"
        \item AdsPriorities3,"Please rank the following advertising qualities in order of their importance to you (by dragging the choices up and down), where 1 is the most important, and 7 is the least important. The advertisement provides useful information"
        \item AdsPriorities4,"Please rank the following advertising qualities in order of their importance to you (by dragging the choices up and down), where 1 is the most important, and 7 is the least important. The advertisement seems trustworthy"
        \item AdsPriorities5,"Please rank the following advertising qualities in order of their importance to you (by dragging the choices up and down), where 1 is the most important, and 7 is the least important. The advertisement is from a company that I like"
        \item AdsPriorities6,"Please rank the following advertising qualities in order of their importance to you (by dragging the choices up and down), where 1 is the most important, and 7 is the least important. The advertisement offers something of value, like a free trial"
        \item AdsPriorities7,"Please rank the following advertising qualities in order of their importance to you (by dragging the choices up and down), where 1 is the most important, and 7 is the least important. The advertisement avoids fluffy or vague language"
        \item AIDangerous,What do you think is the most dangerous aspect of increasingly advanced AI technology?
        \item AIInteresting,What do you think is the most exciting aspect of increasingly advanced AI technology?
        \item AIResponsible,"Whose responsibility is it, <u>primarily</u>, to consider the ramifications of increasingly advanced AI technology?"
        \item AIFuture,"Overall, what's your take on the future of artificial intelligence?"
        \item StackOverflowHasAccount,Do you have a Stack Overflow account?
        \item StackOverflowParticipate,"How frequently would you say you participate in Q&A on Stack Overflow? By participate we mean ask, answer, vote for, or comment on questions."
        \item StackOverflowJobs,Have you ever used or visited Stack Overflow Jobs?
        \item StackOverflowDevStory,Do you have an up-to-date Developer Story on Stack Overflow?
        \item StackOverflowJobsRecommend,How likely is it that you would recommend Stack Overflow Jobs to a friend or colleague? Where 0 is not likely at all and 10 is very likely.
        \item HypotheticalTools1,"Please rate your interest in participating in each of the following hypothetical tools on Stack Overflow, where 1 is not at all interested and 5 is extremely interested. A peer mentoring system"
        \item HypotheticalTools2,"Please rate your interest in participating in each of the following hypothetical tools on Stack Overflow, where 1 is not at all interested and 5 is extremely interested. A private area for people new to programming"
        \item HypotheticalTools3,"Please rate your interest in participating in each of the following hypothetical tools on Stack Overflow, where 1 is not at all interested and 5 is extremely interested. A programming-oriented blog platform"
        \item HypotheticalTools4,"Please rate your interest in participating in each of the following hypothetical tools on Stack Overflow, where 1 is not at all interested and 5 is extremely interested. An employer or job review system"
        \item HypotheticalTools5,"Please rate your interest in participating in each of the following hypothetical tools on Stack Overflow, where 1 is not at all interested and 5 is extremely interested. An area for Q&A related to career growth"
        \item SexualOrientation,"Which of the following do you currently identify as? Please select all that apply. If you prefer not to answer, you may leave this question blank."
        \item RaceEthnicity,"Which of the following do you identify as? Please check all that apply. If you prefer not to answer, you may leave this question blank."
        \item MilitaryUS,Are you currently serving or have you ever served in the U.S. Military?
        \item SurveyTooLong,How do you feel about the length of the survey that you just completed?
        \item SurveyEasy,How easy or difficult was this survey to complete
    \end{itemize}


    \chapter{Lista pytań w ankiecie StackOverflow w roku 2019}\label{app:dod3}

    CareerSat,"Overall, how satisfied are you with your career thus far?"
    JobSat,"How satisfied are you with your current job? (If you work multiple jobs, answer for the one you spend the most hours on.)"
    JobSeek,Which of the following best describes your current job-seeking status?


    ConvertedComp,"Salary converted to annual USD salaries using the exchange rate on 2019-02-01, assuming 12 working months and 50 working weeks."
    DevType,Which of the following describe you? Please select all that apply.
    YearsCodePro,How many years have you coded professionally (as a part of your work)?
    Country,In which country do you currently reside?
    EdLevel,Which of the following best describes the highest level of formal education that you’ve completed?
    Employment,Which of the following best describes your current employment status?
    UndergradMajor,What was your main or most important field of study?
    LanguageWorkedWith,"Which of the following programming, scripting, and markup languages have you done extensive development work in over the past year, and which do you want to work in over the next year?  (If you both worked with the language and want to continue to do so, please check both boxes in that row.)"
    Gender,"Which of the following do you currently identify as? Please select all that apply. If you prefer not to answer, you may leave this question blank."
    OrgSize,Approximately how many people are employed by the company or organization you work for?


    Age,"What is your age (in years)? If you prefer not to answer, you may leave this question blank."


    DatabaseWorkedWith,"Which of the following database environments have you done extensive development work in over the past year, and which do you want to work in over the next year?   (If you both worked with the database and want to continue to do so, please check both boxes in that row.)"
    PlatformWorkedWith,"Which of the following platforms have you done extensive development work for over the past year?   (If you both developed for the platform and want to continue to do so, please check both boxes in that row.)"
    WebFrameWorkedWith,"Which of the following web frameworks have you done extensive development work in over the past year, and which do you want to work in over the next year? (If you both worked with the framework and want to continue to do so, please check both boxes in that row.)"
    MiscTechWorkedWith,"Which of the following other frameworks, libraries, and tools have you done extensive development work in over the past year, and which do you want to work in over the next year? (If you both worked with the technology and want to continue to do so, please check both boxes in that row.)"


    DevEnviron,Which development environment(s) do you use regularly?  Please check all that apply.
    MainBranch,"Which of the following options best describes you today? Here, by ""developer"" we mean ""someone who writes code."""
    Hobbyist,Do you code as a hobby?
    OpenSourcer,How often do you contribute to open source?
    OpenSource,How do you feel about the quality of open source software (OSS)?
    Student,"Are you currently enrolled in a formal, degree-granting college or university program?"
    EduOther,Which of the following types of non-degree education have you used or participated in? Please select all that apply.
    YearsCode,"Including any education, how many years have you been coding?"
    Age1stCode,"At what age did you write your first line of code or program? (E.g., webpage, Hello World, Scratch project)"
    MgrIdiot,How confident are you that your manager knows what they’re doing?
    MgrMoney,Do you believe that you need to be a manager to make more money?
    MgrWant,Do you want to become a manager yourself in the future?
    LastHireDate,When was the last time that you took a job with a new employer?
    ImpSyn,"For the specific work you do, and the years of experience you have, how do you rate your own level of competence?"
    OpSys,What is the primary operating system in which you work?
    Containers,"How do you use containers (Docker, Open Container Initiative (OCI), etc.)?"
    BetterLife,Do you think people born today will have a better life than their parents?
    Extraversion,Do you prefer online chat or IRL conversations?
    SOVisit1st,"To the best of your memory, when did you first visit Stack Overflow?"
    SOVisitFreq,How frequently would you say you visit Stack Overflow?
    SOVisitTo,I visit Stack Overflow to... (check all that apply)
    SOFindAnswer,"On average, how many times a week do you find (and use) an answer on Stack Overflow?"
    SOTimeSaved,"Think back to the last time you solved a coding problem using Stack Overflow, as well as the last time you solved a problem using a different resource. Which was faster?"
    SOComm,Do you consider yourself a member of the Stack Overflow community?
    Trans,Do you identify as transgender?
    Dependents,"Do you have any dependents (e.g., children, elders, or others) that you care for?"


    JobFactors,"Imagine that you are deciding between two job offers with the same compensation, benefits, and location. Of the following factors, which 3 are MOST important to you?"
    WorkWeekHrs,"On average, how many hours per week do you work?"
    WorkPlan,How structured or planned is your work?
    WorkChallenge,"Of these options, what are your greatest challenges to productivity as a developer? Select up to 3:"
    WorkRemote,How often do you work remotely?
    WorkLoc,Where would you prefer to work?
    CodeRev,Do you review code as part of your work?
    CodeRevHrs,"On average, how many hours per week do you spend on code review?"
    UnitTests,Does your company regularly employ unit tests in the development of their products?
    PurchaseHow,"How does your company make decisions about purchasing new technology (cloud, AI, IoT, databases)?"
    PurchaseWhat,"What level of influence do you, personally, have over new technology purchases at your organization?"
    LanguageDesireNextYear,"Which of the following programming, scripting, and markup languages have you done extensive development work in over the past year, and which do you want to work in over the next year?  (If you both worked with the language and want to continue to do so, please check both boxes in that row.)"
    DatabaseDesireNextYear,"Which of the following database environments have you done extensive development work in over the past year, and which do you want to work in over the next year?   (If you both worked with the database and want to continue to do so, please check both boxes in that row.)"
    PlatformDesireNextYear,"Which of the following platforms have you done extensive development work for over the past year?   (If you both developed for the platform and want to continue to do so, please check both boxes in that row.)"
    WebFrameDesireNextYear,"Which of the following web frameworks have you done extensive development work in over the past year, and which do you want to work in over the next year? (If you both worked with the framework and want to continue to do so, please check both boxes in that row.)"
    MiscTechDesireNextYear,"Which of the following other frameworks, libraries, and tools have you done extensive development work in over the past year, and which do you want to work in over the next year? (If you both worked with the technology and want to continue to do so, please check both boxes in that row.)"


    LastInt,"In your most recent successful job interview (resulting in a job offer), you were asked to... (check all that apply)"
    FizzBuzz,Have you ever been asked to solve FizzBuzz in an interview?
    ResumeUpdate,"Think back to the last time you updated your resumé, CV, or an online profile on a job site. What is the PRIMARY reason that you did so?"
    CurrencySymbol,"Which currency do you use day-to-day? If your answer is complicated, please pick the one you're most comfortable estimating in."
    CurrencyDesc,"Which currency do you use day-to-day? If your answer is complicated, please pick the one you're most comfortable estimating in."
    CompTotal,"What is your current total compensation (salary, bonuses, and perks, before taxes and deductions), in `CurrencySymbol`? Please enter a whole number in the box below, without any punctuation. If you are paid hourly, please estimate an equivalent weekly, monthly, or yearly salary. If you prefer not to answer, please leave the box empty."
    CompFreq,"Is that compensation weekly, monthly, or yearly?"
    BlockchainOrg,How is your organization thinking about or implementing blockchain technology?
    BlockchainIs,Blockchain / cryptocurrency technology is primarily:
    ITperson,"Are you the ""IT support person"" for your family?"
    OffOn,Have you tried turning it off and on again?
    SocialMedia,What social media site do you use the most?
    ScreenName,What do you call it?
    SOHowMuchTime,"About how much time did you save? If you're not sure, please use your best estimate."
    SOAccount,Do you have a Stack Overflow account?
    SOPartFreq,"How frequently would you say you participate in Q&A on Stack Overflow? By participate we mean ask, answer, vote for, or comment on questions."
    SOJobs,Have you ever used or visited Stack Overflow Jobs?
    EntTeams,Have you ever used Stack Overflow for Enterprise or Stack Overflow for Teams?
    WelcomeChange,"Compared to last year, how welcome do you feel on Stack Overflow?"
    SONewContent,Would you like to see any of the following on Stack Overflow? Check all that apply.
    Sexuality,"Which of the following do you currently identify as? Please select all that apply. If you prefer not to answer, you may leave this question blank."
    Ethnicity,"Which of the following do you identify as? Please check all that apply. If you prefer not to answer, you may leave this question blank."
    SurveyLength,How do you feel about the length of the survey this year?
    SurveyEase,How easy or difficult was this survey to complete?
\end{appendices}
\thispagestyle{normal}
